---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# metabmc

<!-- badges: start -->
<!-- badges: end -->

`metabmc` is an R package to fit and visualize the meta-uncertainty workflow, as described in the research paper by Schmitt, Radev, & Bürkner(2023). 
By augmenting observed data with tailored simulations, we can mitigate overconfident model selection in the context of Bayesian model comparison.

## Installation

You can install the development version of `metabmc` directly from the GitHub source:

``` {r, eval=FALSE}
install.packages("devtools")
devtools::install_github("marvinschmitt/metabmc")
```

## How to use metabmc

```{r include=FALSE}
# library(ggplot2)
# library(brms)
```

```{r, results='hide', include=FALSE, eval=FALSE}
m1 <- bf(x ~ 0 + arma(p=1, q=0))
m2 <- bf(x ~ 0 + arma(p=0, q=1))
m3 <- bf(x ~ 0 + arma(p=1, q=1))

prior1 <- c(set_prior("normal(0, 0.2)", class = "ar"),
           set_prior("normal(0, 0.2)", class = "sigma"))

prior2 <- c(set_prior("normal(0, 0.2)", class = "ma"),
           set_prior("normal(0, .02)", class = "sigma"))

prior3 <- c(set_prior("normal(0, 0.2)", class = "ar"),
           set_prior("normal(0, 0.2)", class = "ma"),
           set_prior("normal(0, 0.2)", class = "sigma"))

fit1 <- brm(m1, data=LakeHuron, prior = prior1, save_pars = save_pars(all = TRUE))
fit2 <- brm(m2, data=LakeHuron, prior = prior2, save_pars = save_pars(all = TRUE))
fit3 <- brm(m3, data=LakeHuron, prior = prior3, save_pars = save_pars(all = TRUE))
```


```{r example}
library(metabmc)
```

The `metabmc` package uses brms and Stan as a backbone to fit complicated 
Bayesian models with a straightforward interface. The entire computationally intense part of the meta-uncertainty workflow is encapsulated in the function `metabmc`. We can simply input configured `brmsfit` objects along with a arguments that specify the simulation settings.

```{r, results='hide', eval=FALSE}
metabmc_fit <- metabmc(fit1, fit2, fit3, n_sim=20)
```

### Visualizations

Posterior model probabilities obtained from simulation can be visualized with the `plot_simulated_pmp()` function:

```{r,eval=FALSE}
plot_simulated_pmp(metabmc_fit)
```

The posterior predictive distributions of each estimated meta model can be visualized via the `plot_meta_model_density()` function:

```{r,eval=FALSE}
plot_meta_model_density(metabmc_fit)
```

The visualization of estimated predictive mixture based on observed posterior
model probabilities is implemented in the `plot_predictive_mixture()` function.

```{r,eval=FALSE}
plot_predictive_mixture(metabmc_fit)
```

This is usually the endpoint of a meta-uncertainty analysis, as described in the original research paper.


