---
title: "Estimating and visualizing posterior model probability with meta_uncertainty"
author: "Yuga Hikida"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: yes
vignette: >
  %\VignetteIndexEntry{Estimating and visualizing posterior model probability with meta_uncertainty}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
params:
  EVAL: !r identical(Sys.getenv("NOT_CRAN"), "true")
---

```{r, SETTINGS-knitr, include=FALSE}
stopifnot(require(knitr))
options(width = 90)
opts_chunk$set(
  comment = NA,
  message = FALSE,
  warning = FALSE,
  eval = if (isTRUE(exists("params"))) params$EVAL else FALSE,
  dev = "jpeg",
  dpi = 100,
  fig.asp = 0.8,
  fig.width = 5,
  out.width = "60%",
  fig.align = "center"
)
library(brms)
library(metau)
ggplot2::theme_set(theme_default())
data("LakeHuron")
LakeHuron <- LakeHuron - mean(LakeHuron)
```

## Introduction

This vignette provides an introduction on how to estimate and visualize posterior 
predictive distribution of posterior model probability and predictive mixture 
model using simulations with **meta_uncertainty**. The packages uses **brms** 
and **Stan** as a backbone to enable estimation of complicated Bayesian 
model with simple syntax.

Given data $y$ and model $M_j$ $j=1,..,J$, parameterized with $\theta$, we can 
write marginal likelihood of data $y$ given model $M_j$ as:

$$p(y \mid M_j) =\int_{}^{}\,p(y \mid \theta, M_j)p(\theta \mid M_j) \,d\theta$$
Using Bayes rule, we can derive posterior model probability for $M_j$ as:

$$\pi_j :=p(M_j \mid y)= \frac{p(y \mid M_j) p(M_j)} {\sum_{M^{\prime} \in \mathcal{M}}p(y \mid M^{\prime}) p(M^{\prime})}$$

The posterior model probabilities (PMPs) represent the uncertainty over the choice of 
$J$ candidate models. However, they also have uncertainty themselves due to data 
generating process of $y$ with finite samples. Hence, PMPs obtained from data $y$ 
could be overconfident / underconfident about which model to be favoured.

With **meta_uncertainty**, we can obtain distribution of PMPs using simulated 
data $y^{s}$ given true model $M*$ and prior distribution $p(\theta)$. 
We currently support all the framework for three candidate models.

## Posterior distribution of model probability using **meta_uncertainty**

Suppose we have some (centered) time series which we want to approximate with 
either AR(1), MA(1) or ARMA(1,1) model.

```{r}
plot(LakeHuron, type='l')
```
We can fit three models using **brms** as follow.

```{r, results='hide'}
m1 <- bf(x ~ 0 + arma(p=1, q=0))
m2 <- bf(x ~ 0 + arma(p=0, q=1))
m3 <- bf(x ~ 0 + arma(p=1, q=1))

prior1 <- c(set_prior("normal(0, .5)", class = "ar"),
           set_prior("normal(0, .5)", class = "sigma"))

prior2 <- c(set_prior("normal(0, .5)", class = "ma"),
           set_prior("normal(0, .5)", class = "sigma"))

prior3 <- c(set_prior("normal(0, .5)", class = "ar"),
           set_prior("normal(0, .5)", class = "ma"),
           set_prior("normal(0, .5)", class = "sigma"))

fit1 <- brm(m1, data=LakeHuron, prior = prior1, save_pars = save_pars(all = TRUE))
fit2 <- brm(m2, data=LakeHuron, prior = prior2, save_pars = save_pars(all = TRUE))
fit3 <- brm(m3, data=LakeHuron, prior = prior3, save_pars = save_pars(all = TRUE))
```

Estimations of posterior distribution of model probability as well as predictive 
mixture model can be done using all-in-one function `meta_uncertainty`.
We input three `brmsfit` object as arguments along with other arguments which
will be discussed later. Note that to estimate posterior model probability later, 
we need to set the argument `save_pars` accordingly when fitting model with **brms**.

```{r}
meta_uncertainty_fit <- meta_uncertainty(fit1, fit2, fit3, n_sim=20)
```

Alternatively, list of prior distribution, brms formulas can be added as 
arguments. In this case, all the model is fit inside `meta_uncertainty` function.

```{r}
# meta_uncertainty_fit <- meta_uncertainty(list(m1, m2, m3), list(prior1, prior2, prior3), data = LakeHuron, n_sim=20)
```

Firstly, we sample model $M^*$ from $J = 3$ candidates from model prior $p(M)$. 
It is set to be uniform distribution by default indicating all models have equal
probability of being sampled.

Given model $M^*$, we can obtain simulated data $y^{s}$ and simulated model 
implied PMPs as above. This can be written as:

$$\mathbf{\overset{s}{\pi}} := (p(M_1 \mid \overset{s}{y}),\ p(M_2 \mid \overset{s}{y}),\ p(M_3 \mid \overset{s}{y}))$$
We can do this multiple times to get more simulated posterior model probabilities
from all the models, which will be used to estimate the density. In this case we
set number of simulation to be $20$ with `n_sim`.

Visualization of simulated PMPs can be obtained as follow.

```{r}
plot_simulated_pmp(meta_uncertainty_fit)
```

The point in each triangles represent the simulated PMPs implied by each true 
models.

Given simulated PMPs, we can obtain posterior predictive
distribution of posterior model probability, which we call as **meta models** as:

$p(\tilde{\pi} \mid \{\overset{s}{\pi}\}_j) = \int_{}^{} p_j(\pi \mid \tau_j) p(\tau_j \mid \{\overset{s}{\pi}\}_j) d \tau_j$

where $\tau_j$ is the parameter for meta model corresponding to model $j$ and
$\{\overset{s}{\pi}\}_j$ is simulated PMPs implied by $M_j$.

Visualization of estimated meta models can be obtained as follow. Note that we
currently only support logistic normal distribution.

```{r}
plot_meta_model_density(meta_uncertainty_fit)
```

The area with high density is displayed in yellow while low density is displayed 
in purple.

## Predictive mixture model using **meta_uncertainty**

Combining meta models and posterior model probabilities obtained from observed
data $\mathbf{\overset{o}{\pi}} := (\overset{o}{\pi_1}, \overset{o}{\pi_2}, \overset{o}{\pi_3})$, 
we can construct predictive mixture distribution of posterior model probabilities 
by taking weighted sum of meta model by observed posterior model probabilities:

$f(\tilde{\pi}):=\sum_{j=1}^{3} \pi^o_j \ p(\pi \mid \{\pi^s\}_j)$

The visualization of estimated predictive mixture model can be obtained as follow.

```{r, warning=FALSE}
plot_predictive_mixture(meta_uncertainty_fit)
```

The plot shows the predictive mixture model with the position of observed PMPs.
If observed PMPs locate in the area with low density, it suggest that observed
PMPs are overconfident. For our models, it does not seems to be the case.

## Reference
Schmitt, M., Radev, S. T., & Bürkner, P. C. (2023, April). Meta-Uncertainty in Bayesian Model Comparison. In International Conference on Artificial Intelligence and Statistics (pp. 11-29). PMLR.

